Study Level trends

### 2024-04-30 analysis/07_study_change.Rmd
Make sure labels are right

change_group_count_complete <- change_groups %>%
    select(-c(study_id)) %>%
    group_by(across(everything())) %>%
    count() %>%
  mutate(change_description = case_when(
    S == "pos" ~ "increase in richness, not beyond random expectation", 
    S == "neg" ~ "loss of redundancy", 
    S == "0" & Jaccard_base == "neg" ~ "changes in functional space due to turnover",
    n == 6 ~ "no change", 
    .default = NA
  ))

change_group_ses_desc <- change_group_count_ses %>%
   mutate(change_description = case_when(
    S == "pos" ~ "increase in species richness, sometimes leading to increase in functional richness", 
    S == "neg" ~ "loss of redundancy", 
    S == "0" ~ "functional change independent of species richness change",
    n == 7 ~ "no change", 
    .default = NA
  ))

>>>>

change_group_count_complete <- change_groups %>%
    select(-c(study_id)) %>%
    group_by(across(everything())) %>%
    count() %>%
  mutate(change_description = case_when(
    S == "pos" ~ "increase in richness, not beyond random expectation", 
    S == "neg" ~ "loss of redundancy", 
    S == "0" & Jaccard_base == "neg" ~ "changes in functional space due to turnover",
    n == 7 ~ "no change", 
    .default = NA
  ))

change_group_ses_desc <- change_group_count_ses %>%
   mutate(change_description = case_when(
    S == "pos" & n != "7" ~ "increase in species richness", 
    S == "neg" ~ "loss of redundancy", 
    S == "0" ~ "functional change",
    n == "7" ~ "no change", 
    .default = NA
  ))
